Self Regulation Ontology Retest Analyses

### 2018-12-18 code/analysis_nbs/ResponseToReviewers.Rmd

*Response:* We thank the reviewer for providing a potential explanation for the low reliability of the EZ threshold and non-decision time variables for contrasts. In our data the EZ thresholds and non-decision times for contrasts are systematically different than 0 suggesting that they capture a systematic difference instead of the common assumption of noise. Still these contrast measures are much less reliable than non-contrast measures. Similar to the constrasts in raw measures of response times and accuracies, which are less reliable than their non-contrast counterparts, measures do not have to be noise to be unreliable. 
Because the assumption fails we chose not to present this possibility in the manuscript. The details of our analyses on this question can however be found [on:  https://zenkavi.github.io/SRO_Retest_Analyses/output/reports/ResponseToRevisers.nb.html#R1](https://zenkavi.github.io/SRO_Retest_Analyses/output/reports/ResponseToRevisers.nb.html#R1)

```{r echo=FALSE}
rm(list=setdiff(ls(), to_keep))
```

##R1.6
>In our paper, we report ICC(2,1)...

TODO: All results with ICC using ICC(2,1) instead of ICC(3,k)  
- [DONE] recode `get_retest_stats` to report all kinds of ICCs
- [DONE] make new `rel_df` (with both types of ICC for retest paper vars)
- [DONE] make new `boot_df` (with both types of ICC for retest paper vars)
- [DONE] rerun MCMC models with ICC(2,1)
- [DONE] run SRO_Retest_Analyses.Rmd with ICC(2,1) and confirm results don't change
- [DONE] replace fig S3 with new metric scatterplot including icc(2,1)
- [DONE] replace all ICC(3,k)'s in main text

### 2018-12-18 code/SRO_Retest_Analyses.Rmd
rendered new report

```{r, message=FALSE, warning=FALSE, include=FALSE}
from_gh = TRUE
source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/SRO_Retest_Analyses_Workspace.R')
```

@@

tmp_save = tmp %>%
  drop_na() %>% #try removing this in final release
  group_by(contrast, raw_fit, rt_acc) %>%
  summarise(icc2.1_median = quantile(icc2.1, probs = 0.5),
            icc2.1_2.5 = quantile(icc2.1, probs = 0.025),
            icc2.1_97.5 = quantile(icc2.1, probs = 0.975),
            num_vars = n()/1000)

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
set.seed(10394839)
from_gh = TRUE
source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/SRO_Retest_Analyses_Workspace.R')
```

@@

tmp_save = tmp %>%
  drop_na() %>% #try removing this in final release
  group_by(contrast, raw_fit, rt_acc) %>%
  summarise(icc2.1_median = quantile(icc2.1, probs = 0.5),
            icc2.1_2.5 = quantile(icc2.1, probs = 0.025),
            icc2.1_97.5 = quantile(icc2.1, probs = 0.975))
            # num_vars = n()/1000)
